---
title: "plot_marker_intensities_per_image"
author: "LauraK"
date: "2020-03-18"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
# The analysis is done using the ```EBImage``` package. And adapted from Nils Eling's R code

## This workflow analyses pixel intensities for all of the markers to compare the antigen retrieval procedure in HIER buffer of 80C for 45 minutes vs 95C for 30 minutes.

# There are two samples for the two antigen retrieval procedures. Each sample has 5-7 consecutive slices each 2um-thick 

```{r}
library(EBImage)
library(ComplexHeatmap)

# Channel information
panelOri <- read.csv("~Antigen_retrieval_comparison/3D_AR_80_95_comparison.csv", stringsAsFactors = FALSE)
```

# Read image stack for one sample (sample 4) for one antigen retrieval condition (80C, stack of 7 slices)

```{r}
image.list <- list()
image.list$image.80.4.1 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r1_a1_ac.ome.tiff")
image.list$image.80.4.2 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r2_a2_ac.ome.tiff")
image.list$image.80.4.3 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r3_a3_ac.ome.tiff")
image.list$image.80.4.4 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r4_a4_ac.ome.tiff")
image.list$image.80.4.5 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r5_a5_ac.ome.tiff")
image.list$image.80.4.6 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r6_a6_ac.ome.tiff")
image.list$image.80.4.7 <- readImage("20200112_LK_3D_s4_80_ag_comparison_s0_p3_r7_a7_ac.ome.tiff")

image.list$image.95.4.1 <- readImage("20200112_LK_3D_s4_95_ag_comparison_s0_p7_r1_a1_ac.ome.tiff")
image.list$image.95.4.2 <- readImage("20200112_LK_3D_s4_95_ag_comparison_s0_p7_r2_a2_ac.ome.tiff")
image.list$image.95.4.3 <- readImage("20200112_LK_3D_s4_95_ag_comparison_s0_p7_r3_a3_ac.ome.tiff")
image.list$image.95.4.4 <- readImage("20200112_LK_3D_s4_95_ag_comparison_s0_p7_r4_a4_ac.ome.tiff")
image.list$image.95.4.5 <- readImage("20200112_LK_3D_s4_95_ag_comparison_s0_p7_r5_a5_ac.ome.tiff")
```

**Of Note:** In this experiment, the 1st, 15th, 7th-9th, 47th and channel had no antibody included and can be remoeved
Furthermore, the images are ordered based on isotope mass. 
It is therefore crucial to correctly link the antibody to the individual channels.

```{r data-cleaning}
image.list <- lapply(image.list, function(x){x[,,-c(1,3,7,8,9,10,14,15,24,25,26,29,37,40,47)]})
panel <- panelOri[-c(1,3,7,8,9,10,14,15,24,25,26,29,37,40,47),]
```

# Displaying function

```{r normalization}
image.list.norm <- lapply(image.list, function(x){
  for(i in 1:dim(x)[3]){
      x[,,i] <- normalize(x[,,i], inputRange = c(min(x[,,i]), quantile(x[,,i], 0.99)))
  }
  x
})

display(image.list.norm$image.80.4.2)

hist(image.list.norm$image.80.4.1[,,15])
```

# Adaptive thresholding

```{r adaptive-thresholding}
offset = 0.1
# Generate binarized images
image.list.norm.th <- lapply(image.list.norm, function(x){
  disc <- makeBrush(round(min(c(dim(x[,,1])[1], dim(x[,,1])[2]))/3, digits = -1) + 1, "disc")
  disc <- disc / sum(disc)
  cur_bg <- filter2(x, disc)
  x > cur_bg + offset
})
# Smooth to reduce noise
image.list.norm.th.smooth <- lapply(image.list.norm.th, function(x){
  medianFilter(x, size = 3)
})

#display(image.list.norm.th$image.80.4.1)

# Perform segmentation
# Segment images 
image.list.norm.segmented <- lapply(image.list.norm.th.smooth, function(x){
  cur_label <- bwlabel(x)
  cur_label
})

#display(colorLabels(image.list.norm.segmented$image.80.4.2))

# Set all objects smaller than the set pixel size to 0 (background)
# Define minimum size of objects
pixel_size <- 30
image.list.norm.segmented.filter <- lapply(image.list.norm.segmented, function(x){
  x <- combine(lapply(getFrames(x), function(y){
    y[y %in% names(table(y))[table(y) < pixel_size]] <- 0
    y
    }))
  x
})

#display(colorLabels(image.list.norm.segmented.filter$image.80.4.1))

# Calculate signal to noise ratio on normalized images
SNR.adaptive <- mapply(function(image, image.norm.smooth){
  mapply(function(frame.un, frame.norm.smooth){
    mean(frame.un[frame.norm.smooth > 0])/mean(frame.un[frame.norm.smooth == 0])
    },
              getFrames(image), getFrames(image.norm.smooth))
}, 
image.list.norm, image.list.norm.segmented.filter)
```

# Visualize results

```{r SNR-heatmap, fig.height=10, fig.width=8}
#Adaptive thresholding
rownames(SNR.adaptive) <-  panel$channel_target
Heatmap(SNR.adaptive, cluster_columns  = FALSE, 
        col =   c('white','#ccebc5','#a8ddb5','#7bccc4','#43a2ca','#0868ac'),
        cluster_rows = FALSE,
        column_split = ifelse(grepl("\\.80.", colnames(SNR.adaptive)), "HIER buffer 80C for 50 minutes", 
                              ifelse(grepl("\\.95.", colnames(SNR.adaptive)), "HIER buffer 95C for 30 minutes", "HIER buffer 95C for 30 minutes")))

```

```{r}
image.list <- list()
image.list$image.80.5.1 <- readImage("20200111_LK_3D_s5_80_ag_comparison_s0_p5_r1_a1_ac.ome.tiff")
image.list$image.80.5.2 <- readImage("20200111_LK_3D_s5_80_ag_comparison_s0_p5_r3_a3_ac.ome.tiff")
image.list$image.80.5.3 <- readImage("20200111_LK_3D_s5_80_ag_comparison_s0_p5_r4_a4_ac.ome.tiff")
image.list$image.80.5.4 <- readImage("20200111_LK_3D_s5_80_ag_comparison_s0_p5_r5_a5_ac.ome.tiff")
image.list$image.80.5.5 <- readImage("20200111_LK_3D_s5_80_ag_comparison_s0_p5_r6_a6_ac.ome.tiff")
image.list$image.80.5.6 <- readImage("20200111_LK_3D_s5_80_ag_comparison_s0_p5_r7_a7_ac.ome.tiff")

image.list$image.95.5.1 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r1_a1_ac.ome.tiff")
image.list$image.95.5.2 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r2_a2_ac.ome.tiff")
image.list$image.95.5.3 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r3_a3_ac.ome.tiff")
image.list$image.95.5.4 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r4_a4_ac.ome.tiff")
image.list$image.95.5.5 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r5_a5_ac.ome.tiff")
image.list$image.95.5.6 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r6_a6_ac.ome.tiff")
image.list$image.95.5.7 <- readImage("20200110_LK_3D_s5_95_ag_comparison_s0_p4_r7_a7_ac.ome.tiff")
```

```{r data-cleaning}
image.list <- lapply(image.list, function(x){x[,,-c(1,3,7,8,9,10,14,15,24,25,26,29,37,40,47)]})
panel <- panelOri[-c(1,3,7,8,9,10,14,15,24,25,26,29,37,40,47),]
```

```{r normalization}
image.list <- lapply(image.list, function(x){
  for(i in 1:dim(x)[3]){
      x[,,i] <- normalize(x[,,i], inputRange = c(min(x[,,i]), quantile(x[,,i], 0.99)))
  }
  x
})
```

# Adaptive thresholding

```{r adaptive-thresholding}
offset = 0.1
# Generate binarized images
image.list.norm.th <- lapply(image.list, function(x){
  disc <- makeBrush(round(min(c(dim(x[,,1])[1], dim(x[,,1])[2]))/3, digits = -1) + 1, "disc")
  disc <- disc / sum(disc)
  cur_bg <- filter2(x, disc)
  x > cur_bg + offset
})
# Smooth to reduce noise
image.list.norm.th.smooth <- lapply(image.list.norm.th, function(x){
  medianFilter(x, size = 3)
})

# Perform segmentation
# Segment images 
image.list.norm.segmented <- lapply(image.list.norm.th.smooth, function(x){
  cur_label <- bwlabel(x)
  cur_label
})

# Set all objects smaller than the set pixel size to 0 (background)
# Define minimum size of objects
pixel_size <- 30
image.list.norm.segmented.filter <- lapply(image.list.norm.segmented, function(x){
  x <- combine(lapply(getFrames(x), function(y){
    y[y %in% names(table(y))[table(y) < pixel_size]] <- 0
    y
    }))
  x
})


# Calculate signal to noise ratio on normalized images
SNR.adaptive <- mapply(function(image, image.norm.smooth){
  mapply(function(frame.un, frame.norm.smooth){
    mean(frame.un[frame.norm.smooth > 0])/mean(frame.un[frame.norm.smooth == 0])
    },
              getFrames(image), getFrames(image.norm.smooth))
}, 
image.list, image.list.norm.segmented.filter)
```

```{r SNR-heatmap, fig.height=10, fig.width=8}
#Adaptive thresholding
rownames(SNR.adaptive) <-  panel$clean_target
Heatmap(SNR.adaptive, cluster_columns  = FALSE, 
        col =  c('white','#ccebc5','#a8ddb5','#7bccc4','#43a2ca','#0868ac'),
        cluster_rows = FALSE,
        column_split = ifelse(grepl("\\.80.", colnames(SNR.adaptive)), "HIER buffer 80C for 50 minutes", 
                              ifelse(grepl("\\.95.", colnames(SNR.adaptive)), "HIER buffer 95C for 30 minutes", "HIER buffer 95C for 30 minutes")))
```


```{r sessionInfo}
sessionInfo()
```
